Figures

### 2016-05-28 figures/figures.rmd
worked on figures

```{r setup2,echo=FALSE}
orig_sum_labs <- c("peak_time","peak_vir","eq_vir","rel_peak")
new_sum_labs <- c("peak time","peak virulence","equilibrium virulence","relative peak")
fixfac2 <- function(x,atop=FALSE,newlines=FALSE) {
    if (atop) new_sum_labs <-
                  gsub("(.*) (.*)","atop(\\1,\\2)",new_sum_labs)
    factor(x,
           levels=orig_sum_labs,
           labels=new_sum_labs)
}
```

@@

@@

>>>>

```{r setup2,echo=FALSE}
orig_sum_labs <- c("peak_time","peak_vir","eq_vir","rel_peak")
new_sum_labs <- c("peak time","peak virulence","equilibrium virulence","relative peak")
fixfac2 <- function(x,atop=FALSE,newlines=FALSE) {
    if (atop) new_sum_labs <-
                  gsub("(.*) (.*)","atop(\\1,\\2)",new_sum_labs)
    factor(x,
           levels=orig_sum_labs,
           labels=new_sum_labs)
}

@@

### Figure 2.1 - Transmission rate

```{r fig2.1, fig.width=6, fig.height = 4, echo = FALSE, cache = TRUE,dpi = 400}

source("../R/hivFuns.R")
source("../R/Param.R")

returnBeta <- function(lSpvl, parameters){
	with(as.list(c(parameters)),{
		v = 10^lSpvl
		return(hill(K,Bmax,v,a))
	})
}

ss2 <- transform(ss, mean = returnBeta(mean,HIVpars.skeleton),
								 lwr = returnBeta(lwr,HIVpars.skeleton),
								 upr = returnBeta(upr,HIVpars.skeleton))

gg_betatraj <- ggplot(ss2,
                     aes(tvec,mean,ymin=lwr,ymax=upr))+
	geom_line(aes(colour=model,linetype=model),lwd=1)+
	geom_ribbon(aes(fill = model), alpha=0.3)+
	labs(x="time (years)",y=expression(mean~transmission~rate~during~asymptomatic~stage)) +
	theme(axis.title.y = element_text(margin = margin(0,10,0,0)),
		axis.title.x = element_text(margin = margin(10,0,0,0))) +
	facet_wrap(~model, nrow = 2) +
	zero_margin

## scale_x_continuous(limits=c(0,2500))
print(gg_betatraj)

### Figure 2.2 - Duration

```{r fig2.2, fig.width=6, fig.height = 4, echo = FALSE, cache = TRUE,dpi = 400} 
returnDur <- function(lSpvl, parameters){
	with(as.list(c(parameters)),{
		v = 10^lSpvl
		return(hill(v,Dmax,D50,h))
	})
}

ss3 <- transform(ss, mean = returnDur(mean,HIVpars.skeleton),
								 lwr = returnDur(lwr,HIVpars.skeleton),
								 upr = returnDur(upr,HIVpars.skeleton))

gg_durtraj <- ggplot(ss3,
                     aes(tvec,mean,ymin=lwr,ymax=upr))+
	geom_line(aes(colour=model,linetype=model),lwd=1)+
	geom_ribbon(aes(fill = model), alpha=0.3)+
	labs(x="time (years)",y=expression(mean~duration~of~asymptomatic~stage)) +
	theme(axis.title.y = element_text(margin = margin(0,10,0,0)),
		axis.title.x = element_text(margin = margin(10,0,0,0))) +
	facet_wrap(~model, nrow = 2) +
	zero_margin

## scale_x_continuous(limits=c(0,2500))
print(gg_durtraj)

@@

### Figure 3.1

```{r fig3.1, fig.width=8,fig.height=4.8, echo = FALSE, cache = TRUE,dpi = 600}

sL <- transform(sum_list[["sum_mat"]],rel_peak=peak_vir/eq_vir)
sL$model <- factor(sL$model, c("random","pairform+epc", "pairform", "instswitch+epc","instswitch" , "implicit"))

sL.epi <- transform(sL, eq_t = returnBeta(eq_vir,HIVpars.skeleton),
										peak_t = returnBeta(peak_vir,HIVpars.skeleton),
										eq_dur = returnDur(eq_vir,HIVpars.skeleton),
										peak_dur = returnDur(peak_vir,HIVpars.skeleton))

sL.epi <- sL.epi[,-c(3:6)]

mL.epi <- melt(sL.epi,id.vars=c("model","run"))
## horrible hack (but doesn't help); subsample
## w <- which(mL$model=="random")
## mLw <- mL[-sample(w,size=length(w)*9/10,replace=FALSE),]
w.epi.t <- with(mL.epi,which(model=="random" & variable=="eq_t"))
w.epi.d <- with(mL.epi,which(model=="random" & variable=="eq_dur"))
rval.epi.t <- mean(mL.epi$value[w.epi.t])
rval.epi.d <- mean(mL.epi$value[w.epi.d])
mLw.epi <- droplevels(mL.epi[-c(w.epi.t,w.epi.d),])
mLw.epi$variable <- factor(mLw.epi$variable, levels = c("eq_t", "peak_t", "eq_dur", "peak_dur"),
													 labels = c("Equilbrium asymptomatic transmission rate",
													 					 "Maximum transmission rate",
													 					 "Equilibrium duration of asymptomatic stage",
													 					 "Minimum duration of asymptomatic stage"))

gg_univ.epi <- ggplot(mLw.epi,aes(value,model,fill=model))+
	geom_violinh(width=1)+
	facet_wrap(~variable,scale="free_x")+
	guides(fill=guide_legend(reverse=TRUE))+
	labs(y="")+
	geom_point(data=data.frame(model="random",variable=c("Equilbrium asymptomatic transmission rate",
																											 "Equilibrium duration of asymptomatic stage"),
                               value=c(rval.epi.t, rval.epi.d)),pch=22,size=3,show.legend=FALSE) +
	zero_x_margin
print(gg_univ.epi)
